Extreme heterogeneity of influenza virus infection in single cells

### 2018-01-17 paper/paper.tex
added extra info requested by *eLife* for submission of revision

\subsection{Cell lines and viruses}
The following cell lines were used in this study: the human lung epithelial carcinoma line A549 (ATCC CCL-185), the MDCK-SIAT1 variant of the Madin Darby canine kidney cell line overexpressing human SIAT1 (Sigma-Aldrich 05071502), and the human embryonic kidney cell line 293T (ATCC CRL-3216). 
All cells were maintained in D10 media (DMEM supplemented with 10\% heat-inactivated fetal bovine serum, 2 mM L-glutamine, 100 U of penicillin/ml, and 100 \si{\micro}g of streptomycin/ml) at 37 \si{\degreeCelsius} at 5 \% CO\textsubscript{2}.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell} \jdbcomment{This GitHub repository will be made public upon acceptance of the manuscript.}

@@

\begin{suppfile}
\caption{\label{suppfile:cellgenematrix}
The annotated cell-gene matrix in Matrix Market Format.
This is the matrix generated in \texttt{./results/cellgenecounts/} by running the CellRanger analysis in \texttt{align\_and\_annotate.ipynb} in Supplementary~file~\ref{suppfile:code}.
}
\end{suppfile}

>>>>

\subsection{Cell lines and viruses}
The following cell lines were used in this study: the human lung epithelial carcinoma line A549 (ATCC CCL-185), the MDCK-SIAT1 variant of the Madin Darby canine kidney cell line overexpressing human SIAT1 (Sigma-Aldrich 05071502), and the human embryonic kidney cell line 293T (ATCC CRL-3216). 
The A549 cells were tested as negative for mycoplasma contamination by the Fred Hutch Genomics Core.
All cells were maintained in D10 media (DMEM supplemented with 10\% heat-inactivated fetal bovine serum, 2 mM L-glutamine, 100 U of penicillin/ml, and 100 \si{\micro}g of streptomycin/ml) at 37 \si{\degreeCelsius} at 5 \% CO\textsubscript{2}.

@@

\subsection{Computational analysis of single-cell mRNA sequencing data}
Jupyter notebooks that perform all of the computational analyses are available in Supplementary~file~\ref{suppfile:code} and at \url{https://github.com/jbloomlab/flu_single_cell}~\citep{russell2018github}. \jdbcomment{This GitHub repository will be made public upon acceptance of the manuscript.}

@@

\begin{suppfile}
\caption{\label{suppfile:cellgenematrix}
The annotated cell-gene matrix in Matrix Market Format.
This is the matrix generated in \texttt{./results/cellgenecounts/} by running the CellRanger analysis in \texttt{align\_and\_annotate.ipynb} in Supplementary~file~\ref{suppfile:code}.
\jdbcomment{This file is too large for the \textit{eLife} submission system, and so is in the process of being uploaded to DataDryad.}
}
\end{suppfile}
